Contextual Combinatorial Cascading Bandits

### 2016-01-25 contextual combinatorial cascading bandits.tex
update more comparisons

\begin{abstract} 
We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at problem-specific criterion. In recommendation, the stopping criterion might be the first item a user selects. In network, the stopping criterion might be the first edge being blocked in a path. We also considers position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item. We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases. Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, context information and partial observability. We experiment on both synthetic data and real data and show that our algorithm performs well.
\end{abstract}

@@

A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the according reward. When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.

Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need. Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user. Usually, both users and content are represented by feature vectors. User features may contain basic attributes, like age, gender and nationality, and historical behaviors. Content features may contain categories and descriptive information. Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.

In real applications, the cascade model is popular to describe user behaviors in recommender systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, to determine whether a path is blocked, we check from the source to the end and can stop when meeting a blocked edge without need of knowing states of every edge in the path. In both of the two applications, we the feedback of items before some threshold, which is that user selects one item in recommender system and meeting a blocked edge in network routing. We call this kind of feedback as {\it cascading feedback}.

Usually in recommendations, different positions have different values. It is natural to introduce position discounts.

@@

@@

Our work generalizes combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount. Our generalization expands the applicability of this model and we evaluate it on two real-world problems. \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid. They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs; the reason might be that the items with lower preference come first, so the learning agent will collect more data. However, this might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items. Our work extends this part by introducing position discounted parameters. Under our setting, the items with higher UCB will come first. \cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only. In our setting, users and items are represented by feature vectors which is more general.

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. \cite{li2010contextual} studied multi-armed bandit with context information. \cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.

@@

A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit. When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$. Our setting is more specific than theirs. The base arms in a super arm are triggered in list order; only the previous ones are triggered, the base arm can have the chance to be triggered.
Also, they don't consider the contextual information and position discounts.

@@

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$; we call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$. Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be the combined feature vector of base arm $a$ at time $t$. Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. Next according to the user behavior and the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$. For example in recommender systems, the stopping criterion might be the user finds the first interesting item or has checked all items.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$. Following standard assumptions of stochastic MABs, we assume that all reward distributions have R-sub-Gaussian tails for some known constant $R > 0$; formally, for all $\lambda \in \RR$, one has 
$$
\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2)/2.
$$

@@

We also consider the position discount $\gamma_k, k\leq K$. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different values when user clicks on.

@@

@@

The $\alpha$-regret on time $t$ can be written as
$$
R_t = \alpha f(A_t^*, w_t) - f(A_t, w_t),
$$
where $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R_t$.

@@

@@

      \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
      \STATE {Play $\bA_t$ and observe $\bO_t； \bw_t(\ba_k^t), k\in[\bO_t]$}

      \STATE {//Update statistics}
      \STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
      \STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
      \STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
      \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
      \STATE {$\bbeta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
    \ENDFOR {~~$t$}
  \end{algorithmic}
\end{algorithm}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	In particular, by monotonicity and Lipschitz continuity, we have
	$$
		R(t, \bA_t) \leq B \sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a}$, is binary to indicate whether the user has clicked on $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity. (We leave all verifications in the appendix.) Then we have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$ where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{corollary}

\subsubsection{Conjunctive Objective}

The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. In this case, we can derive a slightly better result.

We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

\subsection{Dissutions}

>>>>

\begin{abstract} 
We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at problem-specific criterion. In recommendation, the stopping criterion might be the first item a user selects. In network, the stopping criterion might be the first edge being blocked in a path. We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item. We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases. Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, contextual information and partial observability. We experiment on both synthetic data and real data and show that our algorithm performs well.
\end{abstract}

@@

A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the corresponding reward. When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.

Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive contents to meet specific user's need. Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user. Usually, both users and contents are represented by feature vectors. User features may contain basic attributes, like age, gender and nationality, and historical behaviors. Content features may contain categories and descriptive information. Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.

In real applications, the cascade model is popular to describe user behaviors in recommender systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item until she finds an attractive item and selects it. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, to determine whether a path is blocked, we check from the source node until we meet a blocked edge, where we don't have to know the states of all edges in the path. In both of the two applications, we observe the feedback of items before some threshold, which is user selecting one item in recommender system and meeting a blocked edge in network routing. We call this kind of feedback as {\it cascading feedback}.

Besides, in recommendations, different positions always have different values. In advertisement display, there are different positions in a website, the front middle, the left/right column, and the bottom and the positions in the front middle might charge highest price. Also in search, the first position in the first page for results might be the most important. So it is natural to introduce position discounts.

@@

\begin{table}
	\renewcommand{\arraystretch}{1.1}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		 &context &triggering &position discounts \\
		\hline
		CMAB &no &yes &no \\
		\hline
		CombCascade	&no &yes &no  \\
		\hline
		C$^2$UCB &yes &no &no  \\
		\hline
		C$^3$-UCB(our) &yes &yes &yes \\
		\hline
	\end{tabular}
	\caption{Comparisons of our setting with previous ones }
	\label{table:outline}
\end{table}

@@

A simplified comparison is listed in Table \ref{table:outline}. We will explain in details.

\cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective where the set of feasible actions form a uniform matroid and the reward of an action is $1$ if and only if there is at least an item with weight $1$. The combinatorial cascading bandits of \cite{kveton2015combinatorial} generalized the framework with a {\it CombCascade} algorithm, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective where each feasible action is a chain of items and reward is $1$ if and only if all items have weight $1$. Our work generalizes this model to involve both contextual information and position discounts. The generalization expands the applicability of the model and we evaluate our algorithm on two real-world problems.

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that the user first examines the items with lower preference and is likely to examine more items to find one attractive, so the learning agent will collect more data. However, this result might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items. Our work extends this part by introducing position discounted parameters which can make the items with higher UCBs come first. They also experimented on an imperfect model, DBN, which does not fit their model. Our generalized setting can contain such models. \cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only. In our setting, users and items are represented by general feature vectors.

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. \cite{li2010contextual} studied multi-armed bandit with context information. They introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.

@@

A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit. When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$. Our method can generalize their setting with contextual information. It is hard to introduce position discounts for general combinatorial bandits except when feasible actions are lists, where items are triggered in list order. To introduce position discounts, we focus on the setting where feasible actions are lists.

@@

We formulate the problem of {\em contextual combinatorial cascading bandits} as follows. Suppose we have a finite set $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$; we call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$. Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a} = (u_t, v_a)$ be the combined feature vector of base arm $a$ at time $t$. Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. Next according to the user behaviors under the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$. For example in recommender systems, the stopping criterion might be that the user has found an attractive item or has checked all items.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information including observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent random variables with sub-Gaussian tails and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Following standard assumptions of stochastic MABs, a reward distribution has R-sub-Gaussian tail if for some known constant $R > 0$ and all $\lambda \in \RR$, one has 
$$
\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
$$
Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.

@@

We introduce position discounts $\gamma_k \in [0,1], k\leq K$. For example in website recommendations, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.

@@

The assumption of Lipschitz continuity gives an estimate of changes in reward function. To obtain a good estimation of reward function, the position $k$ with large discount number $\gamma_k$ need a good estimation of $w(a_k)$. This means the positions with large discount numbers are more important to the reward function, or the reward function is more sensitive to these positions. For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.

@@

The $\alpha$-regret of action $A$ on time $t$ can be written as
$$
R(t, A) = \alpha f_t^{\ast} - f(A, w_t),
$$
where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R(t, \bA_t)$.

@@

		\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
		\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
		\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}

		\STATE {//Update statistics}
		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
		\ENDFOR {~~$t$}
	\end{algorithmic}
\end{algorithm}

@@

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has clicked on $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity. (We leave all verifications in the appendix.) Then we have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{corollary}

\subsubsection{Conjunctive Objective}
\label{sec:conj}

The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and the learning agent receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. In this case, we can derive a slightly better result.

We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. It is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

\subsection{Discussions}
